Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-16 edubots_surveys.Rnw
Eliminated by agreement

\begin{figure}[h!tbp]
\begin{center}
<<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
library(forcats)
survey.interaction %>%
    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience

ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
@
\end{center}
\caption{Correlation between age and experience.}
\label{figure:age.vs.exp}
\end{figure}

>>>>

% \begin{figure}[h!tbp]
% \begin{center}
% <<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
% library(forcats)
% survey.interaction %>%
%     mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
%     mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
%     group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience
% 
% ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
% @
% \end{center}
% \caption{Correlation between age and experience.}
% \label{figure:age.vs.exp}
% \end{figure}
